Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-02-15 inst/examples/20170201-manuscript.Rmd
ok

```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=11}
df <- df.full %>% filter(publication_year >= 1640 &
                         publication_year <= 1911) %>%
              group_by(catalog, publication_year) %>%
              summarize(title_length = median(title_length_wordcount),
	      		n = n())

@@

```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=14, fig.height=6}
pics <- list()
for (catalogue in na.omit(unique(df0$catalog))) {

@@

# Add indicator of the publication period
df$period <- cut(df$publication_year,
           breaks = c(1757, 1766, 1775, 1783),
		 include.lowest = TRUE,
		 right = FALSE
		 )
df$period <- gsub("\\[", "", df$period)
df$period <- gsub("\\)", "", df$period)
df$period <- gsub(",", ",", df$period)
df$period <- gsub("\\]", ",", df$period)

@@

```{r Fig7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=12, fig.height=4}

>>>>

```{r Fig4, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=11}
df <- df.full %>% filter(publication_year >= 1640 &
                         publication_year <= 1911) %>%
              group_by(catalog, publication_year) %>%
              summarize(title_length = median(title_length_wordcount),
	      		n = n())

@@

```{r Fig5, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=13, fig.height=6}
pics <- list()
for (catalogue in na.omit(unique(df0$catalog))) {

@@

# Add indicator of the publication period
df$period <- cut(df$publication_year,
           breaks = c(1757, 1766, 1775, 1783),
		 include.lowest = TRUE,
		 right = FALSE
		 )
df$period <- gsub("\\[", "", df$period)
df$period <- gsub("\\)", "", df$period)
df$period <- gsub(",", ",", df$period)
df$period <- gsub("\\]", "", df$period)

@@

```{r Fig7, echo=FALSE, message=FALSE, warning=FALSE, fig.width=11, fig.height=4}
